\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{newtxtext,newtxmath}
\usepackage[left=0.8in,right=0.8in,top=0.55in,bottom=0.75in]{geometry}
\usepackage{etoolbox}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}


\setlength{\parindent}{0pt}
\setlength{\parskip}{0.32em}
\pagestyle{empty}

% Template-style fields
\newcommand{\ApplicantName}{}
\newcommand{\AddressIlineOne}{}
\newcommand{\AddressIlineTwo}{}
\newcommand{\AddressIIlineOne}{}
\newcommand{\AddressIIlineTwo}{}
\newcommand{\EmailField}{}
\newcommand{\PhoneField}{}
\newcommand{\CompanyName}{}
\newcommand{\DateField}{}

\renewcommand{\author}[1]{\gdef\ApplicantName{#1}}
\newcommand{\ProvideAdress}[3]{%
	\ifstrequal{#3}{I}{%
		\gdef\AddressIlineOne{#1}\gdef\AddressIlineTwo{#2}%
	}{%
		\gdef\AddressIIlineOne{#1}\gdef\AddressIIlineTwo{#2}%
	}%
}
\newcommand{\ProvideEmail}[1]{\gdef\EmailField{#1}}
\newcommand{\ProvidePhone}[2]{\gdef\PhoneField{#1}}
\newcommand{\ProvideName}[2]{\gdef\CompanyName{#1}}
\renewcommand{\date}[2]{\gdef\DateField{#1}}

\newcommand{\dotline}{\noindent\rule{\textwidth}{0.45pt}}
\newcommand{\SignatureLine}[2]{
	\vspace{0.8em}
	#1\\[1.1em]
	\noindent\rule{#2}{0.45pt}\\
	\ApplicantName
}

\newlength{\HeaderLeftShift}
\setlength{\HeaderLeftShift}{\dimexpr1in+\hoffset+\oddsidemargin\relax}
\newlength{\HeaderTopShift}
\setlength{\HeaderTopShift}{\dimexpr1in+\voffset+\topmargin+\headheight+\headsep\relax}

\renewcommand{\maketitle}{
\vspace*{\dimexpr-\HeaderTopShift-\fboxsep-1.0em\relax}
\noindent\makebox[0pt][l]{\hspace*{-\HeaderLeftShift}\colorbox{gray!10}{%
\parbox{\dimexpr\paperwidth-2\fboxsep\relax}{%
\hspace*{\HeaderLeftShift}\parbox{\textwidth}{%
\vspace*{\HeaderTopShift}
\begin{center}
{\fontsize{20}{24}\selectfont\bfseries \ApplicantName}\\[0.8em]
\href{mailto:\EmailField}{\EmailField} \quad|\quad
\href{[Your LinkedIn URL]}{LinkedIn} \quad|\quad
\PhoneField \quad|\quad
\AddressIlineOne
\\
\AddressIlineTwo
\end{center}

\vspace{0.25em}
}}}}
\vspace{0.45em}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Your information
\author{[Your Name]}
\ProvideAdress{[Your City, Country]}{}{I}
\ProvideEmail{[Your Email]}
\ProvidePhone{[Your Phone]}{I}

% Company information
\ProvideName{Hiring Manager}{\I}
\ProvideAdress{Siemens}{Erlangen, Germany}{II}

% Date
\date{\today}{I}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle

\DateField

\vspace{0.55em}
\textbf{\CompanyName}\\
\AddressIIlineOne\\
\AddressIIlineTwo

\vspace{0.65em}
Dear Hiring Manager,

I am writing to express my strong interest in the AI Engineer position. I am currently pursuing a Master's degree in Artificial Intelligence at Brandenburg University of Technology, Cottbus, and I offer hands-on experience developing production-oriented AI systems that improve quality, efficiency, and reliability.

During my GenAI internship at Robert Bosch, I developed an agentic RAG solution for the PLM Windchill platform using LangChain and Agno. This solution helped automate quality-assurance workflows and reduced manual testing effort. I also implemented multi-model LLM agent workflows using GPT, Gemini, and Llama to support automated test-case generation.

My background combines AI research depth with practical engineering execution. As the founder of Graspins, I delivered AI assistants and automation solutions for real-world user workflows. Earlier in my career, I developed business intelligence systems and data pipelines in enterprise environments, strengthening my ability to deliver robust solutions from design through deployment.

I would welcome the opportunity to contribute this combination of research rigor and product-focused engineering to your team. Thank you for your time and consideration.

\vspace{2.0em}
\begin{flushright}
Kind Regards,\\[1.0em]
{\fontsize{16}{22}\selectfont\textit{[Your First Name]}}\\[0.4em]
%\ApplicantName
\end{flushright}

\vspace{0.2em}
\textit{Attachment: CV}

\end{document}