\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{newtxtext,newtxmath}
\usepackage[left=0.8in,right=0.8in,top=0.55in,bottom=0.75in]{geometry}
\usepackage{etoolbox}
\usepackage{enumitem}
\usepackage{xcolor}


\setlength{\parindent}{0pt}
\setlength{\parskip}{0.32em}
\pagestyle{empty}

% Template-style fields
\newcommand{\ApplicantName}{}
\newcommand{\AddressIlineOne}{}
\newcommand{\AddressIlineTwo}{}
\newcommand{\AddressIIlineOne}{}
\newcommand{\AddressIIlineTwo}{}
\newcommand{\EmailField}{}
\newcommand{\PhoneField}{}
\newcommand{\CompanyName}{}
\newcommand{\DateField}{}

\renewcommand{\author}[1]{\gdef\ApplicantName{#1}}
\newcommand{\ProvideAdress}[3]{%
	\ifstrequal{#3}{I}{%
		\gdef\AddressIlineOne{#1}\gdef\AddressIlineTwo{#2}%
	}{%
		\gdef\AddressIIlineOne{#1}\gdef\AddressIIlineTwo{#2}%
	}%
}
\newcommand{\ProvideEmail}[1]{\gdef\EmailField{#1}}
\newcommand{\ProvidePhone}[2]{\gdef\PhoneField{#1}}
\newcommand{\ProvideName}[2]{\gdef\CompanyName{#1}}
\renewcommand{\date}[2]{\gdef\DateField{#1}}

\newcommand{\dotline}{\noindent\rule{\textwidth}{0.45pt}}
\newcommand{\SignatureLine}[2]{
	\vspace{0.8em}
	#1\\[1.1em]
	\noindent\rule{#2}{0.45pt}\\
	\ApplicantName
}

\newlength{\HeaderLeftShift}
\setlength{\HeaderLeftShift}{\dimexpr1in+\hoffset+\oddsidemargin\relax}
\newlength{\HeaderTopShift}
\setlength{\HeaderTopShift}{\dimexpr1in+\voffset+\topmargin+\headheight+\headsep\relax}

\renewcommand{\maketitle}{
\vspace*{\dimexpr-\HeaderTopShift-\fboxsep-1.0em\relax}
\noindent\makebox[0pt][l]{\hspace*{-\HeaderLeftShift}\colorbox{gray!10}{%
\parbox{\dimexpr\paperwidth-2\fboxsep\relax}{%
\hspace*{\HeaderLeftShift}\parbox{\textwidth}{%
\vspace*{\HeaderTopShift}
\begin{center}
{\fontsize{20}{24}\selectfont\bfseries \ApplicantName}\\[0.8em]
\EmailField \quad|\quad
LinkedIn: https://www.linkedin.com/in/chandukasireddy/ \quad|\quad
\PhoneField \quad|\quad
\AddressIlineOne
\\
\AddressIlineTwo
\end{center}

\vspace{0.25em}
}}}}
\vspace{0.45em}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Your information
\author{Chandrakiran Reddy Kasireddy}
\ProvideAdress{Berlin, Germany}{}{I}
\ProvideEmail{chandukasireddy02@gmail.com}
\ProvidePhone{+49 176 58483995}{I}

% Company information
\ProvideName{Hiring Manager}{I}
\ProvideAdress{Knowledge Graph CoE, CPIT - SAP}{Berlin, Germany}{II}

% Date
\date{\today}{I}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle

\DateField

\vspace{0.55em}
\textbf{\CompanyName}\\
\AddressIIlineOne\\
\AddressIIlineTwo

\vspace{0.65em}
Dear Hiring Manager,

I am excited to apply for the Lead Developer - Knowledge Graph \& Semantics (f/m/d) role at SAP. I am currently working at Robert Bosch on Gen AI and AI workflows, including RAG pipelines and agentic workflows, where I design and deliver production systems that connect unstructured enterprise content with reliable AI-assisted decisions. In this role, I have built context retrieval services, LLM orchestration pipelines, and robust data processing workflows using Python, LangChain, and multi-model agent setups. Alongside this, I bring strong experience building data-intensive applications, implementing scalable pipeline architectures, and partnering with technical stakeholders to translate business needs into deployable AI solutions.

Your Knowledge Graph CoE mission to ground AI use cases in trusted business context across SAP IT strongly aligns with the systems I enjoy building. I am particularly motivated by the opportunity to contribute to ontology-to-graph pipelines, entity extraction workflows, and hybrid graph-plus-vector retrieval patterns that improve agent quality and explainability at enterprise scale. I would value contributing to a team that combines architecture ownership with strong engineering discipline through code reviews, testing, documentation, and CI/CD. With practical delivery experience, a product mindset, and clear communication in English and German, I am ready to help SAP scale semantic AI capabilities across collaborating LoBs in the EMEA organization.

\vspace{2.0em}
\begin{flushright}
Kind Regards,\\[1.0em]
{\fontsize{16}{22}\selectfont\textit{Chandrakiran Reddy}}\\[0.4em]
%\ApplicantName
\end{flushright}

\vspace{0.2em}
\textit{Attachment: CV}

\end{document}