% DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------
\documentclass[a4paper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{newtxtext,newtxmath}

%----------------------------------------------------------------------------------------
% FONT
%----------------------------------------------------------------------------------------
%\usepackage{fontspec}
%\defaultfontfeatures{Ligatures=TeX}

%----------------------------------------------------------------------------------------
% PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{comment}
\usepackage{amsmath}
\usepackage{url}
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\linespread{1.03}

\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage[left=0.5in,right=0.5in,top=0.4in,bottom=0.4in]{geometry}

\usepackage{tabularx}
\usepackage[final]{microtype}
\usepackage{ragged2e}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*,label=\textbullet,itemsep=1pt,topsep=2pt,parsep=0pt,partopsep=0pt}

% centered version of X column type
\newcolumntype{C}{>{\centering\arraybackslash}X}

% prevent spillover of tabular into next pages
\usepackage{supertabular}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

% custom section handling
\usepackage{titlesec}
\usepackage{multicol}
\setlength{\columnsep}{18pt}
\usepackage{multirow}
\usepackage{fancyhdr}

\newcommand{\entryheader}[4]{%
  \begin{tabularx}{\textwidth}{@{}>{\RaggedRight\arraybackslash}X r@{}}
    \textbf{#1} & \textbf{#2} \\
    \textit{#3} & \textit{#4} \\
  \end{tabularx}%
}

\newenvironment{entrybullets}{%
  \begin{minipage}[t]{0.77\textwidth}
    \begin{itemize}[leftmargin=*,label=\textbullet,align=left]
}{%
    \end{itemize}
  \end{minipage}
}

\fancypagestyle{secondpage}{%
  \fancyhf{}
  \renewcommand{\headrulewidth}{0pt}
  \renewcommand{\footrulewidth}{0pt}
  \fancyfoot[R]{\tiny \today}
}

% CV section styling
\titleformat{\section}{\Large\bfseries\scshape\raggedright}{}{0em}{}[
  \vspace{-9pt}\rule{\linewidth}{1pt}\vspace{-3pt}
]
\titlespacing{\section}{0pt}{9pt}{3pt}

% Portal-safe links (no active PDF annotations)
\newcommand{\safehref}[2]{#2}
\let\href\safehref

% Social icons
\usepackage{fontawesome5}
\newcommand{\extlink}{\raisebox{0.2ex}{\scriptsize\faExternalLink*}}

% Job listing environments
\newenvironment{jobshort}[2]{%
  \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill & #2 \\[3.75pt]
  \end{tabularx}
}{}

\newenvironment{joblong}[2]{%
  \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill & #2 \\[3.75pt]
  \end{tabularx}
  \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut,leftmargin=1em,itemsep=3pt,label=--]
}{%
    \end{itemize}
  \end{minipage}
}

%----------------------------------------------------------------------------------------
% BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty}

%----------------------------------------------------------------------------------------
% TITLE
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{}C@{}}
  \Huge{Chandrakiran Reddy Kasireddy}\\[10pt]
  
    % Rule: Modify the role as per job discription. 
  \large{AI Researcher \& Software Developer}\\[3pt]


  \href{mailto: chandukasireddy02@gmail.com}{\raisebox{-0.05\height}{\faEnvelope} \ chandukasireddy02@gmail.com} \ $|$ \
  \href{tel:+49 176 58483995}{\raisebox{-0.05\height}{\reflectbox{\faPhone}} \ +49 176 58483995} \ $|$ \
  \href{https://www.linkedin.com/in/chandukasireddy/}{\raisebox{-0.05\height}{\faLinkedin} \ Linkedin} \ $|$ \
  \href{https://chandu.graspins.com/}{\raisebox{-0.05\height}{\faLink} \ Portfolio}\\
\end{tabularx}

%----------------------------------------------------------------------------------------
% SUMMARY
%----------------------------------------------------------------------------------------
\section*{PROFILE}
AI researcher and software developer with expertise in AI models, LLM fine-tuning, embeddings, Agentic RAG and AI agents. Strong skills in Python, PyTorch, and TensorFlow for machine learning model development. Passionate about applying AI for Industry 4.0 innovations, digital assistance systems, and process automation.


%----------------------------------------------------------------------------------------
% PROFESSIONAL EXPERIENCE
%----------------------------------------------------------------------------------------
\section*{PROFESSIONAL EXPERIENCE}
\entryheader{AI Engineer}{Jun 2025 -- May 2026}{Robert Bosch}{Stuttgart, Germany}
\begin{entrybullets}
  \item Developed an Agentic AI tool for the PLM Windchill platform using an Agentic RAG framework with \textbf{Agno} and \textbf{LangChain}, cutting manual Quality Assurance.
  \item Increased team productivity by deploying an LLM agent (GPT, Gemini, Llama) that delivered reliable, automated test cases.
  \item Owned end-to-end development of a RAG-agent system, architecting and optimizing the solution to automate QA workflows in PLM.
\end{entrybullets}

\vspace{0.25cm}
\entryheader{Founder}{Jan 2024 -- Sep 2024}{Graspins Pvt Ltd}{Hyderabad, India}
\begin{entrybullets}
  \item Founded a digital solutions firm specializing in Business Intelligence and full-stack development.
  \item Deployed LLM-based AI agents and chatbots to automate client workflows and enhance customer engagement.
\end{entrybullets}

\vspace{0.25cm}
\entryheader{Associate Engineer}{Aug 2023 -- Dec 2023}{I K Technologies}{Hyderabad, India}
\begin{entrybullets}
  \item Designed and implemented a business intelligence dashboard for real-time monitoring of staff attendance using CCTV analytics (92\% accuracy).
  \item Built data pipelines for Microsoft SQL Server, improving data retrieval. Developed SQL based analytics queries to support data-driven decisions.
\end{entrybullets}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------
\section*{EDUCATION}
\begin{tabularx}{\textwidth}{@{}X r@{}}
  \textbf{Brandenburg University of Technology} & \textbf{Oct 2024 -- Present} \\
  \textit{Masters in Artificial Intelligence} & \textit{Cottbus, Germany} \\
\end{tabularx}

\vspace{0.25cm}
\begin{tabularx}{\textwidth}{@{}X r@{}}
  \textbf{Guru Nanak Institutions Technical Campus} & \textbf{Nov 2020 -- May 2024} \\
  \textit{Bachelors in CSE -- Artificial Intelligence and Machine Learning} & \textit{Hyderabad, India} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% POSITION OF RESPONSIBILITIES
%----------------------------------------------------------------------------------------
\section*{POSITION OF RESPONSIBILITIES}
\entryheader{Prasidium Das Studierendenparlament (StuPa)}{Jul 2025 -- May 2026}{Brandenburgische Technische Universit"at Cottbus-Senftenberg}{}
\begin{entrybullets}
  \item Represent the legislative body to university stakeholders and manage all protocols.
  \item Oversee operations and dispute resolution while safeguarding parliamentary rights.
\end{entrybullets}

\vspace{0.25cm}
\entryheader{Chair Person}{Oct 2023 -- Aug 2024}{IEEE Student Branch}{}
\begin{entrybullets}
  \item Established a strong research community at GNI, leading to a 40\% rise in student-led research projects and supporting 50+ paper publications.
  \item Launched and led technical societies, engaging 100+ professional and student members and organizing 10+ technical workshops.
\end{entrybullets}

\vspace{0.25cm}
\newpage
\thispagestyle{secondpage}

\entryheader{Community Lead \ \extlink}{Jul 2022 -- Aug 2023}{Google DSC}{}
\begin{entrybullets}
  \item Led a 3000+ member tech community, organizing workshops, hackathons, and mentorship programs in web development, AI, blockchain, and cloud computing (GCP), fostering innovation, industry collaboration, and career growth.
\end{entrybullets}

\vspace{0.25cm}
\entryheader{Founder \ | \ Community Manager \ \extlink}{Mar 2022 -- Dec 2023}{Feliks Club}{}
\begin{entrybullets}
  \item Founded and managed a dynamic team of 25 individuals, organizing 30+ events including hackathons, startup challenges, workshops, code jams, codethons, boot camps, and tech talks, fostering a culture of innovation and collaboration.
\end{entrybullets}

%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------
\section*{SKILLS}
\setlength{\tabcolsep}{10pt}
\renewcommand{\arraystretch}{1.0}
\begin{tabularx}{\textwidth}{@{}>{\RaggedRight\arraybackslash}X >{\RaggedRight\arraybackslash}X@{}}
  \textbf{AI \& Machine Learning} & \textbf{Data Science \& Analytics} \\
  Generative AI \& LLMs, Agentic AI, LangChain, Agno, LLM Fine-Tuning, Agentic RAG, Graph RAG, NLP, Computer Vision, Semantic Search, Embeddings &
  SQL, Power BI, Data Visualization (Tableau, Matplotlib), Feature Engineering, Business Intelligence, Statistical Analysis \\
  \\[-3pt]
  \textbf{Cloud Technologies} & \textbf{Software Development \& Tools} \\
  AWS, Google Cloud Platform, Oracle Database, Azure SQL Database, Compute \& Clusters, Firebase, DevOps &
  Python, JavaScript, Node.js, Firebase, Git, Docker, CI/CD Pipelines, C++, Conda \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% PUBLICATIONS
%----------------------------------------------------------------------------------------
\section*{PUBLICATIONS}
\sloppy
\noindent\textbf{\href{https://example.com}{Digital Emotions using Sentiment Analysis for Predictive Insights on Customer Recommendations\ \extlink}}\\
\textit{IEEE 5th India Council International Subsections Conference (INDISCON) 2024}

\vspace{0.2cm}
\noindent\textbf{\href{https://example.com}{Statistical Deep Learning Enhancements for Automated Cell Counting using CNNs and Ensemble Methods\ \extlink}}\\
\textit{International Journal of Science \& Engineering Development Research - IJSDR}
\fussy

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\section*{PROJECTS}
\sloppy
\noindent\textbf{\href{https://example.com}{Advanced Anomaly Detection in Meteorology Using k-NN and Autoencoders\ \extlink}}\\
\textit{Statistical Deep Learning}
\begin{itemize}
  \item Developed models to detect unusual weather patterns using k-NN and autoencoders.
  \item The models provide early warnings which help in better planning for weather-related disasters.
\end{itemize}

\vspace{0.15cm}
\noindent\textbf{\href{https://example.com}{Low-Light Biopsy Image Enhancement\ \extlink}}\\
\textit{Deep Learning}
\begin{itemize}
  \item Enhanced visibility and accuracy of biopsy images in challenging low-lighting conditions.
  \item Utilized histogram equalization, computer vision, and filtering to improve quality and reduce noise.
\end{itemize}
\fussy

%----------------------------------------------------------------------------------------
% ACHIEVEMENTS
%----------------------------------------------------------------------------------------
\section*{ACHIEVEMENTS}
{\small
\setlength{\tabcolsep}{8pt}
\renewcommand{\arraystretch}{1.15}
\begin{tabularx}{\textwidth}{@{}>{\RaggedRight\arraybackslash}X >{\RaggedRight\arraybackslash}X >{\RaggedRight\arraybackslash}X@{}}
  \textbf{\href{https://example.com}{Google Cloud Digital Leader\ \extlink}} &
  \textbf{\href{https://example.com}{IBM Data Science Coursera\ \extlink}} &
  \textbf{\href{https://example.com}{Best Startup Pitch Award\ \extlink}} \\
  Certifies understanding of Google Cloud core solutions &
  Professional Certificate - 10 course series &
  For findyourbelongings.com, a social cause portal at IITH \\
  \\[-2pt]
  \textbf{\href{https://example.com}{IJRTI Publication\ \extlink}} &
  \textbf{\href{https://example.com}{EUNICE Challenge Winner\ \extlink}} &
  \textbf{\href{https://example.com}{E-CELL IIT Bombay\ \extlink}} \\
  Hybrid algorithms to optimize terrain feature extraction &
  Optimized future workforce for Industrial Park Schwarze Pumpe &
  Campus Ambassador for Entrepreneurship community \\
\end{tabularx}
}

%----------------------------------------------------------------------------------------
% LANGUAGES
%----------------------------------------------------------------------------------------
\section*{LANGUAGES}
\begin{tabularx}{\textwidth}{@{}XXXX@{}}
  \textbf{English} & \textbf{German} & \textbf{Hindi} & \textbf{Telugu} \\
  Proficient & Basic & Fluent & Native \\
\end{tabularx}

\vfill
%\center{\footnotesize Last updated: \today}
\end{document}
